Community-Conditioned Language Models

### 2020-10-27 paper/paper.tex
Start of model section

\section{Experimental setup}
\subsection{Data Sets}

@@

\subsection{Models}
\subsection{Training scheme}

>>>>

\section{Experimental setup}

\subsection{Data sets}

@@

\subsection{Models}

At the the core of the community-conditioned language model (CCLM) 
is a standard $n$-layer neural sequence encoder 
with token embedding (we experiment with LSTM and transformer encoders).
To condition the model, we additionally train a \emph{community embedding},
which is concatenated with the hidden layer of the sequence encoder
for some layer $l_c \leq n$ and passed through a linear layer, 
which projects the resulting vector back down to the origial hidden size.
For $l_c=0$, the community embedding is concatenated directly to the token embedding.
For this reason, the hidden size of the sequence encoder 
and the size of the token embedding are always the same.

\subsection{Training scheme}
